SIR Model With Testing Flows and Isolation

### 2021-02-22 codes/sir_macpan.Rnw
macpan minor update

<<install the package, echo=T  >>=
# install remotes package if necessary:
while (!require(remotes)) {
    install.packages("remotes")
}
## install development version of bbmle:
if (!require("bbmle") || packageVersion("bbmle") < "1.0.23.5") {
    remotes::install_github("bbolker/bbmle")
}
## install the target package and all its dependencies:
remotes::install_github("bbolker/McMasterPandemic",
                        dependencies = TRUE,
                        build_vignettes = TRUE
)
library(McMasterPandemic)
library(ggplot2); theme_set(theme_bw())
library(cowplot)

>>>>

<<install the package, echo=T  >>=
# install remotes package if necessary:
while (!require(remotes)) {
    install.packages("remotes")
}
## install development version of bbmle:
if (!require("bbmle") || packageVersion("bbmle") < "1.0.23.5") {
    remotes::install_github("bbolker/bbmle")
}
## install the target package and all its dependencies:
remotes::install_github("bbolker/McMasterPandemic",
                        dependencies = TRUE,
                        build_vignettes = TRUE
)

##this works remotes::install_github("bbolker/McMasterPandemic")

library(McMasterPandemic)
library(ggplot2); theme_set(theme_bw())
library(cowplot)
